A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Final edits

Of course, $Random$ does quite poorly. Interestingly, $Popularity$ and
$RandomMap$ have comparable performance and score almost half as well as
$LatentFeature$. The fact that their results are similar is not suprising,
however, since they are both relying entirely on item popularity $\rho$.
$Popularity$ utilizes $\rho$ explicity by connecting each item to one of the
most popular items in the other catalogue. $RandomMap$, on the otherhand,
employs $\rho$ in an identical manner to that by $LatentFeature$. This reveals
that popularity alone accounts for nearly half of $LatentFeature$'s success.

@@

As expected, we find that $OneModel$ outperforms $LatentFeature$. Indeed, one
might ask why $OneModel$ does not score even higher. The performance of
$OneModel$ is limited by the rank reduction stage of the algorithm, which
discards a large amount of information. $LatentFeature$ benefits from this stage
since by discarding dimensions, the subsequent mapping problem becomes more
tractable. Nonetheless, it is interesting that $OneModel$ outperforms
$LatentFeature$ by a about a factor of 2. Given that $OneModel$ is a cheat that
involves perfectly mapped concept spaces, we can consider it a loose upperbound
for $LatentFeature$ (at least when working with 16 dimensions). It might,
therefore, be possible to signficantly improve the performance of
$LatentFeature$ by improving its concept space mapping stage.  At the same time,
it is not at all clear that such a mapping in general even exists. Rather, the
common existence of an approximate mapping is a hypothesis of the authors that
is corroborated by our experimental results for the present dataset.

@@

In this work, we introduced a novel technique for predicting item-item
associations across retailers. This technique employs {\em Topic-Sensitive
PageRank} on a publicly available recommendation graph to generate simulated
user data. With this data, we perform {\em Latent Semantec Indexing} to learn a
latent feature space for items from in a particular online catalogue. By
generalizing the notion of {\em Term Frequency---Inverse Document Frequency}
score, we construct proxy tf-idf vectors for the latent dimensions, or {\em
concepts}, associated with a particular catalogue. This, in turn, allows us to
construct a transformation matrix such that vectors in one catalogue's concept
space can be transformed into another catalogue's concept space. Inter-catalogue
associations can then be made by finding pairs of items that are a minimal
distance apart in a common concept space.

This technique is improved upon by incorporating the notion of item {\em
popularity} $\rho$, which we define in this context to be the logarithm of the
item's degree within its associated recommendation graph. We show that $\rho$
can be used in multiple ways to improve the performance of an inter-retailer
recommender system.

Finally, we compared our latent inter-catalogue recommender system to several
nontrival baseline algorithms and find that it outperforms all of them in both
standard precision and recall of gold-standard inter-catalogue edges as well as
another combination of informative metrics we call {\em 2-precision} and {\em
2-recall}.

Making accurate item-item associations across retailers using only publicly
available information is a challenging problem. The ability to accurately
identity these relationships, however, could potentially provide a retailer or
other service provider with valuable business intelligence.

>>>>

Of course, $Random$ does quite poorly, emphasizing the difficulty of the
problem. Interestingly, $Popularity$ and $RandomMap$ have comparable performance
and score almost half as well as $LatentFeature$. The fact that their results
are similar is not suprising, however, since they are both relying entirely on
item popularity $\rho$.  $Popularity$ utilizes $\rho$ explicity by connecting
each item to one of the most popular items in the other catalogue. $RandomMap$,
on the otherhand, employs $\rho$ in an identical manner to that by
$LatentFeature$. This reveals that popularity alone accounts for nearly half of
$LatentFeature$'s success.

@@

As expected, we find that $OneModel$ outperforms $LatentFeature$. Indeed, one
might ask why $OneModel$ does not score even higher. The performance of
$OneModel$ is limited by the rank reduction stage of the algorithm, which
discards a large amount of information. $LatentFeature$ benefits from this stage
since by discarding dimensions, the subsequent mapping problem becomes more
tractable. Nonetheless, it is interesting that $OneModel$ outperforms
$LatentFeature$ by about a factor of 2. Given that $OneModel$ is a cheat that
involves perfectly mapped concept spaces, we can consider it a loose upperbound
for $LatentFeature$ (at least when working with 16 dimensions). It might,
therefore, be possible to signficantly improve the performance of
$LatentFeature$ by improving its concept space mapping stage.  At the same time,
it is not at all clear that such a mapping in general even exists. Rather, the
common existence of an approximate mapping is a hypothesis of the authors that
is corroborated by our experimental results for the present dataset.

@@

In this work, we introduced a novel technique for predicting item-item
associations across retailers. This technique employs {\em Topic-Sensitive
PageRank} on a publicly available recommendation graph to generate simulated
user data. With this data, we perform {\em Latent Semantec Indexing} to learn a
latent feature space for items in a particular online catalogue. By generalizing
the notion of {\em Term Frequency---Inverse Document Frequency}, we construct
proxy tf-idf vectors for the latent dimensions, or {\em concepts}, associated
with a particular catalogue. This, in turn, allows us to construct a
transformation matrix such that vectors in one catalogue's concept space can be
transformed into another catalogue's concept space. Inter-catalogue associations
can then be made by finding pairs of items that are a minimal distance apart in
a common concept space. This technique is improved upon by incorporating the
notion of item {\em popularity} $\rho$, which we define in this context to be
the logarithm of the item's degree within its associated recommendation graph.
We show that $\rho$ can be used in multiple ways to improve the performance of
an inter-retailer recommender system.

Finally, we compared our latent inter-catalogue recommender system to several
nontrival baseline algorithms. We showed that it outperforms all of them in
standard precision and recall of gold-standard inter-catalogue edges as well as
in two more informative metrics we call {\em 2-precision} and {\em 2-recall}.

Making accurate item-item associations across retailers using only publicly
available information is a challenging problem. The ability to accurately
identify these relationships, however, could potentially provide a retailer or
other service provider with valuable business intelligence.
